%-------------------------
% Resume in Latex
% Author : Neil Ruaro
% Website: https://github.com/eRuaro
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://eruaro.github.io/}{\Large Neil Ruaro}} & Email : \href{mailto:neilruaro@gmail.com}{neilruaro@gmail.com}\\
  \href{https://eruaro.github.io//}{https://eruaro.github.io/} & Mobile : +63-929-236-6004 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {De La Salle University}{Manila, Philippines}
      {Senior High School;  GPA: 3.97 / 4.00}{Jun. 2020 - Jun. 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Omdena}{Remote}
      {Machine Learning Engineer}{May 2021 - Present}
      \resumeItemListStart
        \resumeItem{Potential Solar Power Plant sites in the Philippines}
          {Led the develpoment and deployment of a machine learning application that looks for potential solar power plant sites in the Philippines based on satellite data. \href{https://omdenaph-solar.vercel.app/}{https://omdenaph-solar.vercel.app/}}
      \resumeItemListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Dog Breed Classifier}
      {Implemented convolutional neural networks and
utilized mobile-v-net2 architecture and utilized transfer learning, and deep learning with TensorFlow in order to classify dog
breeds based on image inputs. Carefully picked optimizers and loss variables obtaining an accuracy score of 99 percent. \href{https://github.com/eRuaro/Dog-Breed-Classifier}{https://github.com/eRuaro/Dog-Breed-Classifier}} 
\vspace{0.5mm}

    \resumeSubItem{Music Player}
      {Developed a music player application using Flutter, that accesses your device's local storage. Also supports downloading music from the web. \href{https://github.com/eRuaro/music_player}{https://github.com/eRuaro/music_player}}
      \vspace{0.5mm}
      
    \resumeSubItem{Bulldozer price prediction}
      {Implemented random forest regression
algorithm using supervised machine learning to predict the sale price of bulldozers and assigned 5 risk parameters resulting in a
96 percent accuracy. \href{https://github.com/eRuaro/bulldozer-price-regression}{https://github.com/eRuaro/bulldozer-price-regression}}
\vspace{0.5mm}
\resumeSubItem{Heart disease classification}
{Implemented logistic regression
classification algorithm using supervised machine learning to identify whether one has heart disease or not and assigned 3 risk
parameters resulting in an 85 percent accuracy. \href{ https://github.com/eRuaro/heartdisease-classification}{ https://github.com/eRuaro/heartdisease-classification}}
\vspace{0.5mm}
\resumeSubItem{Rawro chat} 
{Built a mobile chat application with Flutter integrated with a Firebase backend
with integration of Cloud firestore wherein users can log-in / register using their email address. Aside from that users can send
and receive messages and the ability to remove messages. \href{https://github.com/eRuaro/chat_rawro}{https://github.com/eRuaro/chat_rawro}}

  \resumeSubHeadingListEnd
  
%
 %-------OPEN SOURCE CONTRIBUTIONS------
 \section{Open Source Contributions}
 \resumeSubHeadingListStart
 \resumeSubItem{Bloc} {I contribute to open issues on Bloc, one of the most popular state management libaries for Flutter applications. Mainly working on bug fixes.\href{https://github.com/felangel/bloc/}{https://github.com/felangel/bloc/}}
 \vspace{0.5mm}
 \resumeSubItem{Harpy} { I contribute to active open issues on Harpy, a mobile application that enhances your Twitter
experience. Mainly working on UI.\href{https://github.com/robertodoering/harpy}{https://github.com/robertodoering/harpy}}
\resumeSubHeadingListEnd

%
%--------ONLINE COURSE CERTIFICATES-----
\section{Online Course Certificates}
\resumeSubHeadingListStart
\resumeSubItem{Accelerated Computer Science Fundamentals 3 course specialization (University of Illinois via Coursera, 2021)} {Learned Object-Oriented programming with C++ and how it is applied to the development of the C++ Standard Template Library.
Learned how to implement various data structures such and algorithms such as Linked-List, HashMaps, Graphs, and Tree
Traversals. \href{https://www.coursera.org/specializations/cs-fundamentals}{https://www.coursera.org/specializations/cs-fundamentals}}
\vspace{0.5mm}
\resumeSubItem
{Data Analysis with Python (freeCodeCamp, 2021)} {Learned how to do data analysis with Python with the numpy, pandas, and matplotlib libraries. \href{https://www.freecodecamp.org/learn/data-analysis-with-python/}{https://www.freecodecamp.org/learn/data-analysis-with-python/}}
\vspace{0.5mm}
\resumeSubItem
{CS50x (Harvard via EdX, 2020)} {Learned foundational computer science concepts and the art of programming using C, and
Python. \href{https://cs50.harvard.edu/college/}{https://cs50.harvard.edu/college/}}
\resumeSubHeadingListEnd

%
%--------ARTICLE POSTS---------------------
\section{Article Posts}
\resumeSubHeadingListStart
\resumeSubItem{The Basics of using and testing Cubits for State Management in Flutter (Flutter):} {Wrote and published a tutorial article
(1000+ views) on how to get started on using the cubit state management approach in Flutter, with TDD.  \href{https://neilruaro.hashnode.dev/using-cubit-for-managing-states-in-flutter}{https://neilruaro.hashnode.dev/using-cubit-for-managing-states-in-flutter}}
\resumeSubHeadingListEnd
%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Dart, Python, C++}
     \hfill
     \textbf{Technologies}{: Flutter, Tensorflow, Scikit-Learn, FastAPI, Typer, Qt}
   }
   \item{\textbf{Developer Tools}{: Git, VS Code, Android Studio, Qt Creator, WSL}}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
